R Notebook

### 2019-04-30 study2/vacc_manyBelief_study2_overpar.Rmd
update sourcing for loading study 2 data

```{r tidy, include = F}
# load data
d_all <- read.csv("../data/study2_data.csv")[-1]

# reformat to match previous analyses (i.e., 2 rows per participant)
d_demo <- d_all %>% 
  select(workerId, condition, gender, age, ethnicity, education, job, income,
         political_party, political_beliefs, eligible_pretest, 
         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
         children_youngest_posttest, plan_parent_posttest,
         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
         starts_with("comments"), starts_with("duration"))
d_pre <- d_all %>% 
  select(workerId, ends_with("_pretest")) %>%
  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
            starts_with("attention_"), starts_with("comments"), 
            starts_with("duration"))) %>%
  rename_all(funs(gsub("_pretest", "", .))) %>%
  mutate(phase = "pre")
d_post <- d_all %>% 
  select(workerId, ends_with("_posttest")) %>%
  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
            children_youngest_posttest, plan_parent_posttest,
            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
            starts_with("comments"), starts_with("duration"))) %>%
  rename_all(funs(gsub("_posttest", "", .))) %>%
  mutate(phase = "post")

d <- bind_rows(d_pre, d_post) %>% 
  gather(question, response, -c(workerId, phase)) %>%
  mutate(phase = factor(phase,
                        levels = c("pre", "post")),
         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
         # NOTE: "response" has already been reverse coded!
         question = factor(question),
         scale = factor(gsub("_.*$", "", question),
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert"))) %>%
  full_join(d_demo) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
  distinct()

# how many left?
# d %>% distinct(workerId, condition) %>% count(condition)
```

```{r scores, include = F}
# score all scales
d_scored <- d %>%
  select(workerId, condition, phase, scale, response,
         gender:duration_posttest) %>%
  group_by(workerId, condition, phase, scale) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(mean = mean(response, na.rm = TRUE)) %>%
  ungroup() %>%
  distinct()
```

@@

```{r}
fit_pre <- brm(
  vaccIntent ~ overpar * medSkept * diseaseSevere + (1|workerId),
  prior = set_prior("normal(0,.5)", class = "b"),
  family = Beta(),
  data = d_bn %>% 
    mutate(vaccIntent = rescale_beta(vaccIntent, -3, 3), workerId = 1:nrow(d_bn)),
  control = list(adapt_delta = .90, max_treedepth = 15),
  chains = 2,
  cores = 2
)
```

```{r}
summary(fit_pre)
```

>>>>

```{r tidy, include = F}
source("../scripts/load-data-s2.R")
```

@@

```{r}
# fit_pre <- brm(
#   vaccIntent ~ overpar * medSkept * diseaseSevere + (1|workerId),
#   prior = set_prior("normal(0,.5)", class = "b"),
#   family = Beta(),
#   data = d_bn %>% 
#     mutate(vaccIntent = rescale_beta(vaccIntent, -3, 3), workerId = 1:nrow(d_bn)),
#   control = list(adapt_delta = .90, max_treedepth = 15),
#   chains = 2,
#   cores = 2
# )
```

```{r}
# summary(fit_pre)
```

### 2019-04-30 study2/vmb_model_preds.Rmd
update sourcing for loading study 2 data

```{r load and tidy study 3 data, include = F}
# load data
d_all <- read.csv("../data/study2_data.csv")

# reformat to match previous analyses (i.e., 2 rows per participant)
d_demo <- d_all %>% 
  select(workerId, condition, gender, age, ethnicity, education, job, income,
         political_party, political_beliefs, eligible_pretest, 
         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
         children_youngest_posttest, plan_parent_posttest,
         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
         starts_with("comments"), starts_with("duration"))
d_pre <- d_all %>% 
  select(workerId, ends_with("_pretest")) %>%
  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
            starts_with("attention_"), starts_with("comments"), 
            starts_with("duration"))) %>%
  rename_all(funs(gsub("_pretest", "", .))) %>%
  mutate(phase = "pre")
d_post <- d_all %>% 
  select(workerId, ends_with("_posttest")) %>%
  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
            children_youngest_posttest, plan_parent_posttest,
            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
            starts_with("comments"), starts_with("duration"))) %>%
  rename_all(funs(gsub("_posttest", "", .))) %>%
  mutate(phase = "post")

d <- bind_rows(d_pre, d_post) %>% 
  gather(question, response, -c(workerId, phase)) %>%
  mutate(phase = factor(phase,
                        levels = c("pre", "post")),
         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
         # NOTE: "response" has already been reverse coded!
         question = factor(question),
         scale = factor(gsub("_.*$", "", question),
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert"))) %>%
  full_join(d_demo) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
  distinct()

# how many left?
d %>% distinct(workerId, condition) %>% count(condition)

# score all scales
d_scored <- d %>%
  select(workerId, condition, phase, scale, response,
         gender:duration_posttest) %>%
  group_by(workerId, condition, phase, scale) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(Mean = mean(response, na.rm = TRUE)) %>%
  ungroup() %>%
  distinct()

>>>>

```{r load and tidy study 3 data, include = F}
source("../scripts/load-data-s2.R")
